%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Membership \& Activities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member \& Director of Finance} % Affiliation/role
    {Scientific Association of Industrial Engineering} % Organization/group
    {Tehran, Iran} % Location
    {Oct. 2020 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Modified the financial sector and used new tools such as Excel and Power BI to report financial activities.}
        \item {In cooperation with the sponsorship department, a number of sponsors in the industry were attracted to support the association's programs.}
        \item {Designed advertising packages.}
        \item {Created and updated the statute of Scientific Association of Industrial Engineering with the cooperation of other core members.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member of Editorial Board} % Affiliation/role
    {``MASAAF'' Student-Scientific Journal (Amirkabir University of Technology)} % Organization/group
    {Tehran, Iran} % Location
    {Sep. 2019 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item{Collecting and writing the latest information related to various fields of industrial engineering and publishing it in the journal.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Santoor Player and Band Leader} % Affiliation/role
    {``Tanin'' Music Band} % Organization/group
    {Tehran, Iran} % Location
    {Sep. 2017 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Performed in official university ceremonies}
        \item {Performed in faculty ceremonies and celebrations}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
