%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Selected Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Undergraduate Thesis} % subtitle
    {Credit Card Fraud Detection Using Supervised Learning Methods} % Title
    { } % Location
    {Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Seven supervised machine learning methods were used on 2 million credit card transactions in order to find the best fraud detection model.}
        \item {The SMOTE method was used to overcome the problem of dataset imbalance.}
        \item {Robust Scaling was identified as the best method for scaling the data.}
        \item {By evaluating the results of MCC and AUROC, Random Forest model was selected as the best model for predicting fraudulent transactions.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Individual Project} % subtitle
    {Spotify Music Taste Discovery} % Title
    { } % Location
    {Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extracted ``Discover Weekly'' playlist's data from Spotify.}
        \item {After pre-processing, a radar chart was drawn indicating the music genre tendency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {``Modeling and Database'' course project} % subtitle
    {Financial Database} % Title
    { } % Location
    {Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a database in SQL server for the ``Finance Department of SAIPA''}
        \item {The data used was provided by the Finance Department of SAIPA Corp.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Individual Project} % subtitle
    {TSE Stocks Analysis} % Title
    { } % Location
    {Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Tehran stocks market analysis done on all available stock tickers.}
        \item {The data was derived from official TSE (Tehran Stock Exchange) website by using data scraping tools}
        \item {The obtained data was stored in a database}
        \item {Using machine learning methods, tickers' behavior during future 7 days were predicted.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SAIPA Project} % subtitle
    {Vehicle Specification Clustering} % Title
    { } % Location
    {Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Using k-means algorithm with the aid of PCA analysis, a segmentation was done based on all available cars' specifications in Iran's market.}
        \item {The data used was provided by ``Center of Strategic Studies of SAIPA''.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SAIPA Project} % subtitle
    {SAIPA Financial Dashboard} % Title
    { } % Location
    {Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A dashboard was created for the biggest automobile company in Iran which showed all financial information of that company between 2015 and 2020.}
        \item {The information in this dashboard includes the financial statements of SAIPA and were collected by the Finance Department.}
        \item{The results were presented to the senior management of SAIPA during a working meeting.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}


\begin{cvparagraph}
%---------------------------------------------------------
   
\end{cvparagraph}
\begin{cvparagraph}
%---------------------------------------------------------
   
\end{cvparagraph}


\begin{cvparagraph}

%---------------------------------------------------------
\textbf{Note: }These projects are only a selection of all completed projects. Please visit \underline{\href{https://peymanfarahani.herokuapp.com}{my website}} to see the complete information of all projects.
\end{cvparagraph}